Psychological Needs During Intergroup Contact

### 2022-03-08 Methods-and-Results.tex
code display fix
M & R re-run

We tested the most general contact hypothesis in two steps. First, we
assessed whether more intergroup interactions were related to to more
positive outgroup attitudes. Second, we tested whether a potential
positive effect on outgroup attitudes depended on the interaction
quality (jointly with the number of interactions). We find that neither
the number of interactions nor the number of daily diary responses with
an interaction were significantly related with the average outgroup
attitudes (all \textbar{} \textit{r} \textbar{} \textless{} 0.03, all
\textit{p} \textgreater{} 0.887). However, we did find a medium sized
correlation between the participants' Average Interaction Quality and
their Average Outgroup Attitudes (\textit{r} = \hl{X.XX}, \textit{p} =
\hl{X.XXX}. And when considering the number of interactions and average
interaction quality jointly in a linear regression, we additionally find
a statistically significant interaction term (\textit{b} = -0.05,
\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34), where
in our sample with an increasing number of interactions the positive
effect of average interaction quality becomes weaker (also see Table
\ref{tab:intergroupGeneralTblLong}). We additionally used a multilevel
regression to check whether having an interaction with an outgroup
member had a situational (i.e., contemporaneous) effect within the
participants. We find that having an outgroup interaction is indeed
associated with significantly more positive outgroup attitudes within
the participants (\textit{b} = 2.48, \textit{t}(1200) = 4.36, \textit{p}
\textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even after
controlling for having an interaction with a non-Dutch (which did not
relate to outgroup attitudes independently; For full results see Table
\ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials
B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate the the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation}.
Thus, in our first data we find mixed results, where outgroup contacts
show a positive effect on outgroup attitudes in the moment but these
results do not translate into average differences between participants
(even tough the average number of interactions does seem to interact
with average interaction quality to predict outgroup attitudes).
However, it should be noted that the between-participant analyses in the
aggregated form are based on a small sample size.

@@

\faQuestionCircle~Are we sure that we don't want some sort of
bootstrapped indirect effect?

>>>>

We tested the most general contact hypothesis in two steps. First, we
assessed whether more intergroup interactions were related to to more
positive outgroup attitudes. Second, we tested whether a potential
positive effect on outgroup attitudes depended on the interaction
quality (jointly with the number of interactions). We find that neither
the number of interactions nor the number of daily diary responses with
an interaction were significantly related with the average outgroup
attitudes (all \textbar{} \textit{r} \textbar{} \textless{} 0.03, all
\textit{p} \textgreater{} 0.887). However, we did find a medium sized
correlation between the participants' Average Interaction Quality and
their Average Outgroup Attitudes (\textit{r} = 0.55, \textit{p} = 0.010.
And when considering the number of interactions and average interaction
quality jointly in a linear regression, we additionally find a
statistically significant interaction term (\textit{b} = -0.05,
\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34), where
in our sample with an increasing number of interactions the positive
effect of average interaction quality becomes weaker (also see Table
\ref{tab:intergroupGeneralTblLong}). We additionally used a multilevel
regression to check whether having an interaction with an outgroup
member had a situational (i.e., contemporaneous) effect within the
participants. We find that having an outgroup interaction is indeed
associated with significantly more positive outgroup attitudes within
the participants (\textit{b} = 2.48, \textit{t}(1200) = 4.36, \textit{p}
\textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even after
controlling for having an interaction with a non-Dutch (which did not
relate to outgroup attitudes independently; For full results see Table
\ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials
B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate the the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation}.
Thus, in our first data we find mixed results, where outgroup contacts
show a positive effect on outgroup attitudes in the moment but these
results do not translate into average differences between participants
(even tough the average number of interactions does seem to interact
with average interaction quality to predict outgroup attitudes).
However, it should be noted that the between-participant analyses in the
aggregated form are based on a small sample size.

@@
